Wikipedia Text Mining and Entropy Analysis

### 2019-02-15 wiki_entropy/wiki_clustering.Rmd
imputation work and organizing

@@

FEATURES <- c(1:144)
for (i in c(1:144)) {
  FEATURES[i] <- paste(FEATURES[i], "A", sep = "")
} #get all WALS features in correct syntax

>>>>

```{r word order}
wiki_gs <- gs_title("Wikipedia_relative5")
wkpd <- gs_read(wiki_gs) 
LANGUAGES <- wkpd$Language

FEATURES <- c(82:97)
for (i in c(1:length(FEATURES))) {
  FEATURES[i] <- paste(FEATURES[i], "A", sep = "")
} #get all word order WALS features in correct syntax

wo_df <- wf %>% 
  filter(language %in% LANGUAGES) %>%
  select(-wals.code, -latitude, -longitude, -glottocode, -`84A`)

wo_df <- wo_df[rowSums(is.na(new_wf)) < 6,] %>%
  as_data_frame() %>%
  group_by(language) %>%
  slice(1) %>%
  gather(feature, value, `82A`:`97A`) %>%
  group_by(feature) %>%
  mutate(value = factor(value))

imputed_wo <- wo_df %>%
  select(language, feature, value) %>%
  ungroup() %>% 
  spread(feature, value) %>% 
  column_to_rownames("language") %>%
  sapply(as.factor) %>%
  as_data_frame() %>%
  MIMCA(ncp = 3, maxiter = 999)

imputed_wo <- as.data.frame(imputed_result[[1]][[99]])

## convert this to work with imputed_wo
wf_many_langs <- wf_df %>%
  group_by(feature) %>%
  summarise(n = sum(!is.na(value))) %>%
  filter(n > 60)

@@

FEATURES <- c(1:144)
for (i in c(1:length(FEATURES))) {
  FEATURES[i] <- paste(FEATURES[i], "A", sep = "")
} #get all WALS features in correct syntax
